The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-10 analysis/paper/paper.qmd
Change lemmatised ngram separator to space

## Bigrams
emu_bigrams <- emu |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", lemma = TRUE) |> 
  unite(ngram_lemma, w_1_lemma, w_2_lemma, sep = "_", remove = FALSE)

>>>>

emu_bigrams <- emu |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", lemma = TRUE) |> 
  unite(ngram_lemma, w_1_lemma, w_2_lemma, sep = " ", remove = FALSE)
